\documentclass[12pt, a4paper]{article}
\usepackage[affil-it]{authblk} % author institution
\usepackage[backend=biber]{biblatex}

\addbibresource{reference.bib}

\title{\textbf{Research Methodology II Report}}
\author{Tran Phong Binh (Student ID: 110062421)}
\affil{Advisor: Chair Professor Jang-Ping Sheu}
\date{\today}

\begin{document}

\maketitle

I have grown a lot in terms of academic research abilities in the past year at the Department of Computer Science in National Tsing Hua University. This report consists of two main sections: the progress I made, and my study plan to draft the Master's thesis in late February 2023.

As soon as I joined HSCC Lab, I participated in Delta Electronics's anomaly detection project, researching three papers on Bayesian optimization \cite{BHF10, HRGNTV19, SKKS12}, implementing Gaussian Process Hedge algorithm, and presented four articles on Generative Adversarial Network (GAN) \cite{HN21, LSLTKW21, QXX19, XDZ19}. Apart from this, I enrolled in five Computer Science courses with at least four top class A+, whilst monitoring and grading homeworks and the final exam as a teaching assistant for Design and Analysis of Algorithms lectured by Chair Professor Sheu. Moreover, I pushed hard in self-learning, progressing 50\%, 75\%, and 100\% in Stanford's Convex Optimization, MIT's Artificial Intelligence and Linear Algebra, respectively. Regarding the thesis, I studied 16 publications in 5G scheduling, narrowing the research topic to resource allocation in ultra-reliable low latency communications (URLLC) puncturing systems, inventing an approximation algorithm by total unimodularity, and have been working on simulations\footnote{https://github.com/phogbinh/5g}.

I have three prime goals for the next semester: finishing course credits, reading 80 academic papers, and completing the thesis's simulations. First and foremost, I attend Natural Language Processing Lab. by Professor Jyun-Sheng Chang to experiment learning-based techniques on my research problem. Secondly, I take on five papers and discuss with my Professor once per week. Thirdly, I kickstart thesis writing, finalizing simulation environment to reproduce others' work and compare performance, aiming to publish on IEEE conferences like INFOCOM and ICC.

\printbibliography

\end{document}
